A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-11 survey.tex
conclusions updated

As the list in the previous section indicates, Real-Time Strategy games are an excellent testbed for AI techniques, which pose a very large list of open problems. As Section \ref{sec:competition} has shown, the current top performing programs to play RTS games such as StarCraft still rely mainly on hard-coded strategies. It is still possible to perform strongly, or even win, one of these competitions simply by finding a hard-coded strategy that no other bot has a predefined counter-strategy for. Additionally, good human players are still clearly superior to the best computer programs.

@@

As argued before, addressing these open research questions would not just lead to better RTS game playing bots, but would bring significant advances to many other areas of artificial intelligence. This is so because RTS games embody many characteristics of many other problems appearing in many areas of AI (such as robotics, multiagent systems, etc.).

>>>>

As the list in the previous section indicates, Real-Time Strategy games are an excellent testbed for AI techniques, which pose a very large list of open problems. As Section \ref{sec:competition} has shown, the current top performing programs to play RTS games such as StarCraft still rely mainly on hard-coded strategies. It is still possible to perform strongly, or even win, one of these competitions simply by finding a hard-coded strategy that no other bot has a predefined counter-strategy for. Additionally, good human players are still clearly superior to the best computer programs. Compared to other genres of game AI, this is one of the few cases where bots simply have to improve to become more believable and thus more fun to play against for human players.

@@

As argued before, addressing these open research questions would not just lead to better RTS game playing bots, but would provide means to improve many other complex AI components, not solely focussing on games. This would apply to many areas that are in need of real-time decision components working under uncertainty in the form of incomplete and/or noisy information, such as  e.g. robotics and assistance systems.
%bring significant advances to many other areas of artificial intelligence. This is so because RTS games embody many characteristics of many other problems appearing in many areas of AI (such as robotics, multiagent systems, etc.).
